\chapter{BACKGROUND AND LITERATURE REVIEW}

% (20\% of Report Length)

% a. Must be paraphrased without plagiarizing

% b. Must include the base papers\cite{Adhikari2020Dec}, and support the rationale of the project

% c. Must highlight the strengths and shortcomings of the works performed by other authors

\section{Background Study}

Traditional science education, dependent on textbooks, lectures, and physical labs, often faces limitations due to resource constraints, high costs, and safety issues. These challenges are especially evident in under-resourced schools, where practical scientific experiences are limited.
LabXplorerX addresses these issues by offering an innovative platform with interactive simulations in chemistry, physics, electronics, and astronomy. It provides a virtual space for conducting experiments, visualizing data, and engaging with scientific concepts, aiming to enhance traditional learning methods.

Additionally, LabXplorerX includes learning capsules, which function like blogs where users can access quizzes, share PDFs, and resources. This feature supports a more comprehensive and interactive learning experience, bridging gaps in practical science education and setting a new standard for STEM learning.
\section{Literature Review}
\subsection*{Teacher perception of Olabs pedagogy}
OLabs, as name says, offers a robust web-based platform encompassing simulations, animations, tutorials, and assessments, designed to enhance interactive and accessible learning experiences outside traditional laboratory settings. Emphasizing student-centered learning, inquiry-based approaches foster essential skills such as scientific thinking, evidence-based reasoning, and creative problem-solving, which are fundamental for knowledge creation and retention \cite{chandrashekhar2020teacher}.
\subsection*{How Khan Academy is changing the rules of education}
This paper briefly describes how can an online learning platfrom change the way our education system worka and improve on it.
\begin{itemize}
    \item Khan Academy offers free, online instructional videos covering various subjects, allowing students to learn at their own pace and revisit concepts.
    
    \item The platform uses analytics to provide real-time feedback, enhancing personalized learning experiences for both teachers and students.
    
    \item Khan Academy promotes a flipped classroom model where students watch videos at home and engage in problem-solving and discussions in class, fostering deeper understanding and collaboration.
    
    \item It democratizes education by providing high-quality instruction globally, irrespective of geographic location or socioeconomic status.
    
    \item The platform challenges traditional educational paradigms and suggests new possibilities for delivering effective education in the digital era.
\end{itemize}
Khan Acadamy being one of the main motivation for onile learning and educating.
\cite{thompson2011khan}
\subsection*{PhET: Interactive simulations for teaching and learning physics}
Perkins et al. (2006) introduce PhET, a collection of interactive simulations designed to enhance the teaching and learning of physics. These simulations aim to make abstract concepts more accessible and understandable through dynamic visualizations and interactive models. The authors emphasize the effectiveness of PhET in promoting conceptual understanding by allowing students to manipulate variables and observe real-time outcomes, thereby bridging the gap between theoretical concepts and practical application. They discuss the development process, which involves collaboration between physicists, educators, and software developers to ensure accuracy and educational efficacy. The article highlights PhET's versatility in catering to diverse learning styles and educational settings, promoting active learning and engagement \cite{perkins2006phet}.

\subsection*{An Introduction to HTML5 Game Development with Phaser.js}
It provides a comprehensive guide to creating 2D games using the Phaser.js framework. It covers setting up a development environment, understanding fundamental game concepts, and managing game states and assets. The book teaches how to implement physics and collision detection, create animations and visual effects, design user interfaces, and integrate audio. It emphasizes practical, project-based learning, guiding readers through real game development scenarios. Additionally, it offers debugging, optimization techniques, and deployment strategies for various platforms, making it an essential resource for both beginners and experienced developers looking to master HTML5 game development with Phaser.js \cite{faas2017introduction}.

\subsection*{The Role of Digital Simulations in STEM Education}
This review focuses on the role of digital simulations in STEM education, emphasizing their benefits in teaching complex scientific concepts. The paper discusses various types of simulations, including those for physics, chemistry, and biology, and their impact on student learning and engagement. The authors argue that digital simulations can bridge the gap between theoretical knowledge and practical application, fostering a deeper understanding of STEM subjects \cite{smith2020digital}.

\subsection*{Unity 3D: A Comprehensive Overview}
Unity 3D is a widely used game development platform that offers a robust environment for creating both 2D and 3D games. The platform is known for its versatility and user-friendly interface, which makes it accessible for both beginners and experienced developers. Unity 3D provides a wide range of tools and features that facilitate the creation of interactive and immersive experiences. Key aspects of Unity 3D include:
\begin{itemize}
    \item \textbf{Cross-Platform Development:} Unity allows developers to build games and simulations for various platforms, including Windows, macOS, iOS, Android, and consoles, with minimal adjustments.
    
    \item \textbf{Asset Management:} The platform includes a comprehensive asset management system, enabling the easy integration of 3D models, textures, animations, and audio.
    
    \item \textbf{Physics and Collision Detection:} Unity offers built-in physics engines and collision detection systems, essential for creating realistic interactions and behaviors within games.
    
    \item \textbf{Scripting and Customization:} Unity supports scripting, allowing developers to create custom game logic, interactions, and behaviors.
    
    \item \textbf{User Interface Design:} Unity provides tools for designing user interfaces, including menus, buttons, and HUD elements, which are crucial for enhancing user experience.
    
    \item \textbf{Real-Time Rendering:} The platform includes a powerful rendering engine that supports high-quality graphics and real-time visual effects, enhancing the visual appeal of games and simulations.
\end{itemize}
Unity 3D extensive documentation, active community, and support for various assets and plugins make it a preferred choice for developing interactive and educational applications \cite{johnson2021unity}.