%==============================Abstract Page=================================================
\chapter*{\centerline{ABSTRACT}}
\addcontentsline{toc}{chapter}{ABSTRACT}
\thispagestyle{plain} 
% Abstract (200 to 250 Words)
\vspace{-0.5cm}

LabXplorerX is an innovative web application designed to revolutionize science education through an interactive and immersive learning experience. Built with modern technologies like React, Express, and Postgres, the platform offers a seamless, responsive interface that caters to students' needs. At its core are real-time simulations powered by Phaser.js and Unity 3D, enabling students to engage with scientific concepts in a visually dynamic and interactive way. LabXplorerX also features a vast library of science-related articles, quizzes, and assessments, encouraging both individual learning and evaluation. The platform introduces Capsules, which serve as modular learning units combining simulations, quizzes, comments, and curated resources, providing a comprehensive learning environment. Users can add their favorite capsules to a personalized list for easy access, promoting a customized learning experience. Through integrated collaboration tools, including real-time comments on simulations and capsules, LabXplorerX fosters a community of inquisitive learners. With a robust system architecture, supported by detailed feasibility studies, and a secure authentication module, the platform is designed for scalability, reliability, and security, making it an effective and engaging tool for modern science education.
\\\\
\textbf{Keywords:} \textit{Interactive, Collaboration, Simulation}
%=============================================================================================
% (a) Inclusion of three to four Keywords (Lexicographical Order)
% \newpage
% \chapter*{\centerline{AKNOWLEDGEMENT}}
% We would like to extend our heartfelt gratitude to the esteemed teachers in the \thedepartment at \thecampus for their invaluable support and guidance throughout the development of our social network application.

% First and foremost, we would like to express our deepest appreciation to \thesupervisor and \theprogramcoordinator, both our project supervisor and program coordinator, for their unwavering commitment,mentorship to our project. Their expertise and profound knowledge in this field have been very helpful in shaping our technical skills and providing invaluable insights of the projects.

% Furthermore, we would like to extend our gratitude to the entire faculty of the \thedepartment. Their dedication to fostering creativity, critical thinking, and technical proficiency has been useful in our project's development. The support and guidance received from our teachers have empowered us to transform our vision into a reality.

% Your unwavering belief in our abilities and your constant encouragement have been the driving force behind our project. Your passion for education and commitment to our growth have left an indelible impact on our personal and professional development.


% Sincerely,\\
% \theauthor\\
% \thedepartment\\
% \thecampus\\
\newpage